### 2014-03-20 paper/abstract.tex
paper work, adding a new figure

\begin{abstract}
3D printers offer extraordinary flexibilty in prototyping the shape and mechanical function of objects.  However, in spite of recent work, a 3D printer's role in prototyping \emph{interactivity} is still not clear.  While macro-scale digital fabrication devices cannot manufacture electronics in-place, we propose a general technique for redirecting active components through the core and onto the surface of 3D printed interactive objects using a series of tubes.  We describe the design space of tubes and hollow chambers for interaction design: there are a variety of types, topologies, and inserted media for tubes that can be leveraged to create diverse inputs and outputs.  We present a technique and design tool for routing tubes of various topologies through the interior of 3D printed parts.  Our design tool is integrated into a 3D model manipulation program.  There are two distinct routing algorithms.  One allows users to select begin and end points for tubes, then uses A* path routing and physics-based simulation to minimize the bending energy of routed paths.  The second allows users to enter a description of paths to follow: for this we developed a novel neon sign routing algorithm and offer proof of its optimality.  We present several totally tubular prototypes we created using this tool to show its flexibility and potential, as well as to explore new points in the tube design space.
\end{abstract}

>>>>

\begin{abstract}
3D printers offer extraordinary flexibilty in prototyping the shape and mechanical function of objects.  However, a 3D printer's role in prototyping interactive objects is still not clear.  We propose a general technique for adding interactivity by removing interior material to form pipes and cavities. These can be used to sense input and generate haptic as well as visible output. We describe the design space of pipes and hollow chambers for interaction design: there are a variety of types, topologies, and inserted media for pipes that can be leveraged to create diverse inputs and outputs.  We present a technique and design tool for routing pipes of various topologies through the interior of 3D printed parts.  Our design tool is integrated into a 3D model manipulation program.  There are two distinct routing algorithms.  One, for creating particular points of interaction or integrating with existing electronics, allows users to select begin and end points for pipes, then uses A* path routing and physics-based simulation to minimize the bending energy of routed paths.  The second, for creating, e.g., novel neon signs, allows users to enter a description of paths to follow: for this we developed a novel routing algorithm and offer proof of key traits.  We present several totally tubular prototypes we created using this tool to show its flexibility and potential, as well as to explore new points in the pipe design space.
\end{abstract}

### 2014-03-20 paper/appendix.tex
paper work, adding a new figure

\newpage
\appendix
\section{Injection Measurements}
We injected the copper a distance of 1.16m (according to the spiral length calculator at http://www.giangrandi.ch/soft/spiral/spiral.shtml ) in a spiral whose cross-section was a square of area $9mm^2$.  I suspect that is about as far as we can go without using a vacuum at the end.

>>>>

\newpage
\appendix

\section{Proof of Theorem 1}

\begin{theorem} \label{thm:graphness}
 $G' = (V, E')$ is a connected, semi-Eulerian graph for which $E \subseteq E'$.
\end{theorem}

\begin{proof}
$E \subseteq E'$ : we never remove edges from $E$ in our algorithm.  $\therefore E \subseteq E'$.

$G' = (V, E')$ is connected : if $G'$ is not connected, $\exists G_i = (V_i, E_i) \subset G', u \in V_i, v\in V \setminus V_i$ s.t. $u$ is not reachable from $v$.  $G_i \not\in G_{dis}$, because we create edges connecting $G_j, G_k \forall G_j, G_k \in G_{dis}$ and only remove an edge $e_{dupe} = (u, v)$ from $E_{conn}$ once we determine that $u$ is reachable from $v$ along edges $E' \cup E_{conn-min}$.  $\therefore G_i \not\in G_{dis}$.  This implies that $G_i$ was not initially disconnected from $G$, because by definition $G_{dis}$ is the set of all disconnected subgraphs of $G$.  We cannot have disconnected $G_i$ from $G$ because $E \subseteq E'$.  Thus, a contradiction.  $\therefore G' = (V, E')$ is connected.

$G' = (V, E')$ is semi-Eulerian : Each edge $e$ in our minimum weight matching connects a unique pair of vertices $v_i, v_j \in V_{odd}$ by the definition of minimum weight matching.  Each edge $e = (v_i, v_j) \in E_{circuit-min}$ adds one to the degree of $v_i$ and $v_j$, causing them to be of even degree. $|V_{odd}| \% 2 = 0$ by the handshake lemma, $\therefore$ all edges can be paired.  When we remove $e_{temp} = (start, end)$ from $E'$, we cause those vertices, which were of even degree by the above process, to be of odd degree.  Thus, all vertices except $start$ and $end$ (which are of odd degree) are of even degree.  $\therefore G'$ is semi-Eulerian.
\end{proof}

\section{Injection Measurements}
We injected the copper a distance of 1.16m (according to the spiral length calculator at http://www.giangrandi.ch/soft/spiral/spiral.shtml ) in a spiral whose cross-section was a square of area $9mm^2$.  I suspect that is about as far as we can go without using a vacuum at the end.
